An Empirical Analysis of C Preprocessor Use

### 2000-01-18 macros/papers/emp-use-2.tex
Added explanation of Perl's outlier-dom for fig 2, unknown identifier.

>>>>

A notable outlier in Figure~\ref{fig:categorization} is the \pkg{perl}
package's high occurrence of unknown identifiers in macro definitions.
At almost 31\%, these kinds of macro definitions are over three times
more prevalent in \pkg{perl} than in \pkg{mosaic}, the package that is
second in this metric.  This excessiveness results from \pkg{perl} using 
the preprocessor to conditionally redefine over one thousand global
symbols to have the prefix ``Perl_'' for avoiding link-time collisions
when its interpreter is embedding in another application.  Typical
such macro definitions are:

\begin{verbatim}
    #define Sv          Perl_Sv
    #define Xpv         Perl_Xpv
\end{verbatim}
